RLWE Homomorphic Encryption Scheme

### 2023-08-17 Paper.tex
Update Paper.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{listings}

\begin{document}

\title{RLWE Homomorphic Encryption Scheme}
\author{Aidan (@CodeByAidan) | Madalina Bolboceanu (@mbolboceanu)}
\date{8/16/2023}
\maketitle

@@

See more: \url{https://eprint.iacr.org/2012/144.pdf}

@@

Thank you to the author of the original code:
\begin{itemize}
    \item Madalina Bolboceanu (\url{https://github.com/mbolboceanu})
\end{itemize}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{url}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
}
\urlstyle{same}

\title{RLWE Homomorphic Encryption Scheme}
\author{
  Aidan (\href{https://github.com}{@CodeByAidan}) \\
  Mădălina Bolboceanu (\href{https://github.com/mbolboceanu}{@mbolboceanu}) \\
  Miruna Roșca (\href{https://github.com/MirunaRosca}{@MirunaRosca}) \\
  Radu Țițiu (\href{https://github.com/rtitiu}{@rtitiu})
}
\date{\today}

\begin{document}
\maketitle

@@

See more:

\begin{itemize}
    \item \href{https://eprint.iacr.org/2012/144.pdf}{"Somewhat Practical Fully Homomorphic"}, 
    \item \href{https://bit-ml.github.io/blog/post/homomorphic-encryption-toy-implementation-in-python/}{"Homomorphic Encryption: a Toy Implementation in Python"}
\end{itemize}

@@

Thank you to the authors of the original code:
\begin{itemize}
    \item Mădălina Bolboceanu (\url{https://github.com/mbolboceanu})
    \item Miruna Roșca (\url{https://github.com/MirunaRosca})
    \item Radu Țițiu (\url{https://github.com/rtitiu})
\end{itemize}
